\LARGE \bf A Pipeline for Assembling Collision and Near-Collision Dashcam Footage Datasets

### 2021-03-28 paper.tex
reword title, add todo regarding AUC in figure

\title{\LARGE \bf
A Pipeline to Assemble (Near-)Collision Footage Datasets
}

@@

In order to evaluate the importance of acquiring data from multiple geographical locations and under varying driving conditions around the world, we have manually collected a dataset of 223 video clips on which we will test the existing collision anticipation model, DSARNN. This dataset is comprised of 97 positive and 126 negative videos. Most of these videos represent road scenes from North America, Europe and Russia which have noticeably different characteristics than those in Taiwan. To prepare our data we follow the steps outlined by Chan et. al \cite{chan2016anticipating}. Namely, we trim videos such that they are 5 seconds long, sampled at 20 FPS, and the collision occurs at frame 90. This trimming and sampling functionality is provided within a configuration of our pipeline, \texttt{smallcorgi\_exporter.yml}. In our experiments we train the DSARNN model on features produced by running a pre-trained VGG on each full frame and the cropped objects within the frame \cite{DBLP:journals/corr/SimonyanZ14a}. This is denoted VGG+RNN+F+D-con. in the original publication. We note that this data includes manually annotated bounding boxes, so there will be no error imposed by using automated vehicle detection and localization models.

@@

\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.4\textwidth]{prcurve.png}
		\caption{}
		\label{fig:pr_curve}
\end{figure}

>>>>

\title{\LARGE \bf
A Pipeline for Assembling Collision and Near-Collision Dashcam Footage Datasets
}

@@

In order to evaluate the importance of acquiring data from multiple geographical locations and under varying driving conditions around the world, we have manually collected a dataset of 223 video clips on which we will test the existing collision anticipation model, DSARNN. This dataset is comprised of 97 positive and 126 negative videos. Most of these videos represent road scenes from North America, Europe and Russia which have noticeably different characteristics than those in Taiwan. To prepare our data we follow the steps outlined by Chan et. al \cite{chan2016anticipating}. Namely, we trim videos such that they are 5 seconds long, sampled at 20 FPS, and the collision occurs at frame 90. This trimming and sampling functionality is provided within the pipeline configuration \texttt{smallcorgi\_exporter.yml}. In our experiments we train the DSARNN model on features produced by running a pre-trained VGG on each full frame and the cropped objects within the frame \cite{DBLP:journals/corr/SimonyanZ14a}. This is denoted VGG+RNN+F+D-con. in the original publication. We note that this data includes manually annotated bounding boxes, so there will be no error imposed by using automated vehicle detection and localization models.

@@

\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.4\textwidth]{prcurve.png}
		\caption{\todo{Write caption, fix label (I don't think the term AUC is correct here since this value is actually the average precision from the training code)}}
		\label{fig:pr_curve}
\end{figure}
